Review: Adaptive Introgression Expanded the Genetic Base of Crops during post-Domestication Spread

### 2018-02-09 paper.tex
more edits added

The decreasing cost of genome-wide resequencing and availability of reduced-representation genotyping (\emph{e.g.}, GBS and RAD-Seq), combined with new analytical methods, has facilitated comprehensive study of introgression across a number of species (\textbf{Table 1}). \gmj{Are there newer resequencing methods to discuss here?  DART-Seq, etc?}
\lwang{I think it is fine to mention two of these methods, it is not our focus.}
High-density marker data can be used with haplotype-based and other methods to assign specific genomic regions to a taxon of origin and identify introgression across taxa \cite{Martin2015,Price2009,Lawson2012,pease2015,rosenzweig2016,geneva2015}.
The methods reviewed here do not include those marginally estimating introgression\slash migration rate as a component of demographic history (\emph{e.g.}, Approximate Bayesian Computation (ABC) \cite{beaumont2002}, diffusion approximations for demographic inference ($\delta a\delta i$) \cite{gutenkunst2009}, isolation with migration models \cite{hey2004}, and a series of methods utilizing the sequentially Markovian coalescent (PSMC, MSMC and SMC++) \cite{li2011, schiffels2014, terhorst2017}). 
Rather, we focus on methods that explicitly identify introgressed genomic segments based on the extent of differentiation, on patterns of nucleotide/haplotype sharing, and phylogenetic relationships.
%We focus here on analytical prospects and limitations and introduce only a few representatives of each category.

First, introgressed segments are expected to show low differentiation from their source population.
The $F_{st}$ and $d_{XY}$ statistics and their derivates including $G_{min}$ \cite{geneva2015} and $RND_{min}$\cite{rosenzweig2016} gauge differentiation. 
The former two statistics are insensitive to rare migrants and therefore lack power to detect recent introgression, while the latter two overcome this limitation.
Additionally, $RND_{min}$ accounts for variable mutation rate, which is detected based on branch length to an outgroup:

@@

 \begin{equation}
 	RND_{min} = \frac{d_{min}}{d_{out}}
 \end{equation}
where $d_{min}$ is the minimum sequence distance between haplotypes in species X and Y and $d_{out}$ equals $(d_{XO} + d_{YO})/2$, the average sequence distance between each species and the outgroup ($O$).

@@

\gmj{Li, are you familiar with the analytical tools MIGRATE-N and BAYESASS?  Rieseberg comapres these two to STRUCTURE at some length in the discussion of this paper:
https://biology.unm.edu/Whitney/Whitney%20Reprints/Scascitelli%20et%20al%202010.pdf
Should we include these two methods, even in passing, in this portion of the paper?}
\lwang{Garrett, I donot know these two methods. I am reading the paper you mentioned here.}

@@

\gmj{This paragraph about application seems like it might not belong in this section.  Maybe it should be a part of the introduction?  Or, maybe each of these examples could be mentioned directly following the method(s) that was used in the study?}
Application of these approaches across a number of plant and animal species suggests introgression can play an adaptive role.
For example, introgression from ancient hominins (\emph{e.g.}, Neanderthals and Denisovans) to humans has been detected at loci controlling skin pigmentation, defense against pathogens, and toleration of high altitude (reviewed in \cite{Racimo2015});
introgression of wing coloration loci has conferred M\"{u}llerian mimicry
(a type of mimicry in which two unpalatable species resemble one another, compounding the efficacy of their repellant signal)
%\mbh{I would explain a bit more here...wing coloration loci, protects against predation...}
across butterfly species \cite{Heliconius2012}; introgression has spread insecticide resistance across mosquito species \cite{Norris2015}, and introgression across \emph{Mimulus} (\emph{i.e.}, monkeyflower) species has resulted in adaptation to pollinator preference and contributed to speciation \cite{Stankowski2015}.

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=17.35cm]{li_figure.png}
	\caption{Li's caption here.}
	\label{fig:introgressionMaize}
\end{figure}

@@

The story of Asian rice (\emph{Oryza sativa}) domestication is still debated.
Certain genetic and archaeobotanical evidence points toward independent domestications of the two prominent varietal groups \emph{japonica} and \emph{indica} from the wild species \emph{Oryza rufipogon} (\emph{rufipogon} hereafter) in the Yangtze Basin of China 7000 BP and the Indian Ganges plain 4000 BP, respectively \cite{fuller2010consilience}, with possibly another domestication event giving rise to \emph{aus} in Bangladesh or central India \cite{civavn2015three}.
Other studies support a single domestication occurring 8,200-13,500 BP in the Yangtze Basin, with later divergence of \emph{japonica} and \emph{indica} \cite{molina2011molecular, Huang2012}.
Huang and colleagues \cite{Huang2012} developed a genetic map of rice variation, which they used to measure genetic distance between wild and domesticated rices at and around domesication loci for various geographical locations, finding that \emph{japonica} was likely domesticated in the Pearl River area of Guangxi province, China (just south of the Yangtze Basin), and that \emph{indica} was likely the result of hybridization between \emph{japonica} and local \emph{rufipogon} populations in Southern and South-eastern Asia.
In a re-examination of these same data, \cite{civavn2015three} found evidence supporting independent domestications of \emph{japonica}, \emph{indica}, and \emph{aus}, as well as a hybrid origin (\emph{japonica} x \emph{aus}) of variety \emph{aromatic}.
A third analysis \cite{choi2018multiple} compared these two disparate results and the methods utilized therein, concluding that domestication alleles (including \emph{LABA1}, \emph{PROG1}, and \emph{sh1}) arose via a single domestication event of \emph{japonica}, and that these alleles introgressed into several wild \emph{rufipogon} subpopulations which became the progenitors to the other Asian rice varieties.
 %Also, Huang includes the following quote: "We noticed that many loci with strong signals of selection were nearly identical in both indica and japonica where FST between indica and japonica was extremely low, indicating that introduction of traits during domestication has in many cases involved introgression events."

@@

The findings of \cite{choi2018multiple} run in parallel with a hypothesis posited by Vaughan and colleagues in 2008 \cite{vaughan2008evolving}.
%Vaughan and colleagues \cite{vaughan2008evolving} posit a hypothesis combining elements of both theories.
According to this hypothesis, the non-shattering allele (\emph{sh1}) arose in a single cultivated rice population and then introgressed into many diverse cultivated populations (some \emph{japonica}-like, some \emph{indica}-like) in the region.
This would have facilitated the subsequent spread of other domestication alleles among those populations.
As these domesticated populations then spread into new environments, they would have received introgressions from locally-adapted wild relatives, retaining alleles that improved fitness (in agreement with \cite{second1982origin}).
Both Vaughan and Choi support the role of introgression between domesticated Asian rice and locally-adapted wild \emph{rufipogon} populations in the development and dispersal of Asian rice into new environments.

Despite many conditions favorable to their prevalence, to date, individual examples of adaptive alleles naturally introgressing into domesticated Asian rice are not clear (though \cite{zhao2010genomic} emphasizes the necessity of research on this topic).
Contemporary populations of wild rices show evidence of this history of local adaptation.
Wild \emph{rufipogon} and \emph{nivara} both maintain high genotypic and phenotypic diversity and exhibit locally-adaptive traits (\emph{rufipogon} is adapted to forested wetland environments, whereas \emph{nivara} is adapted to dryer conditions and has life cycle adaptations to survive grazing pressure), suggesting that either offered (and offers) adaptive genetic potential.
Domesticated varieties have likewise adapted to local environments.
The \emph{japonicas} are generally more adapted to upland temperate regions (and are split into subgroups adapted to more temperate or more tropical conditions), the \emph{indicas} are best suited for tropical lowland environments, \emph{aus} matures quickly and tolerates drought stress, and two deepwater varieties (\emph{rayada} and \emph{ashwina}) are said to be selected for the environment along the Ganges river \cite{vaughan2008evolving, garris2005genetic}.
Crop-wild hybridization is frequent enough that nuisance weedy hybrids commonly arise amongst cultivated populations and must be managed with difficulty \cite{vaughan2008evolving}.
However, as with many other domesticated crops, gene flow between wild and domesticated rices is highly asymmetric (estimates of wild rice admixture in domesticated rice are less than 5 percent \cite{wang2017asian}).
This asymmetry is due in part to the closed floret architecture of the domesticated rice, which hinders outcrossing.
Still, barriers to crop-to-wild introgression may have been less severe during early domestication as the inbreeding reproductive system of domesticated rice would not have been as firmly established \cite{vaughan2008evolving}.
Furthermore, the contemporary distribution of wild rice does not capture the full range and diversity of wild rice during early domestication and range expansion of Asian rice.

@@

\rowcolors{2}{white}{gray!25}
\begin{center}
\caption{List and brief description of recently developed methods and examples of empirical studies employing these methods.} \label{tab:tools}
\begin{tabular}{0.8\textwidth}{}
\\\toprule  
\rowcolor{white}
{\bf methods}	& {\bf data type } &	{\bf reference} &  {\bf empirical studies } \\ \midrule

@@

\end{tabular}
\end{center}
\end{table}

@@

A framework in which crops are domesticated from a single wild population or even a single species is an oversimplification when introgression is extensive during crop geographic expansion.
The addition of ongoing gene flow to our understanding of crop demography could therefore bear importantly on fundamental questions of crop domestication:

\subsection*{What is the progenitor of a crop?}
Depending on the extent of post-domestication gene flow with new wild relatives, identification of a crop's progenitor can be complicated or confounded entirely.
Introgression between a crop and newly-encountered taxa decreases divergence from these donors.
This signal could be mistaken for origin rather than gene flow.
For example, when determining a single origin of maize from \emph{parviglumis}, Matsuoka and colleagues \cite{matsuoka2002single} identified a paradox: while \emph{parviglumis} is found exclusively in the lowlands of southwest Mexico, maize with allele frequencies most similar to \emph{parviglumis} was found in the highlands of the Mexican Central Plateau.
Several years later, van Heerwaarden \emph{et al.} \cite{vanHeerwaarden2011} resolved the paradox by determining that widespread introgression in the highlands from \emph{mexicana}, which is closely related to \emph{parviglumis}, has caused maize from this region to appear ancestral.
Similarly, extensive post-domestication adaptive introgression from  potato wild relatives long obscured this crop's origin.
Recent work has shown that, following the original domestication event of \emph{Solanum tuberosum} in the central Andes, potato received introgression from as many as four additional species during colonization of the highest elevations of the Andes and the lowlands of the Chilean coast \cite{Spooner2014, Gavrilenko2013, Hardigan2017}.

@@

\subsection*{When was a crop domesticated?}
Estimates of the timing of initial domestication are often based on levels of sequence divergence between a crop and populations of its presumed progenitor (\emph{e.g.}, \cite{matsuoka2002single, molina2011molecular}).
In highly introgressed domesticates, these estimates will be based on comparison of both crop and introgressant haplotypes to those of the presumed progenitor.
In such cases, divergence time is a mixture of time since domestication and time since split of the progenitor and the introgressing taxon.
This phenomenon, in combination with divergence of crop samples from true ancestral crop populations, ongoing evolution of crop progenitors, and problems with assuming evolution under a molecular clock \cite{Zeder2006}, may help explain discrepancies between domestication dates based on genetic and archaeological data.
More accurate estimates of the timing of domestication may be obtained from genetic data by excluding loci that show signatures of introgression or by explicitly including estimates of introgression when modeling a crop's demographic history.

\subsection*{How was genome-wide diversity shaped by domestication?}

Measurement of the strength of the initial domestication bottleneck may also be impacted by adaptive introgression during the spread of crops.
Crop wild relatives have distinct demographies when compared to domesticates and may therefore have contrasting effective population sizes ($N_e$).
The influence of wild relative introgression on estimates of the domestication bottleneck will depend on a number of factors including the magnitude of gene flow, the $N_e$ of the introgressing taxon, and the strength of selection on haplotypes following introgression.
For example, substantial introgression at neutral loci from a wild taxon with a historically higher $N_e$ will lead to underestimates of the overall strength of the domestication bottleneck.

\subsection*{What candidate genes were targeted by selection during domestication?}
Loci targeted by selection during domestication can be identified through so-called ``bottom-up'' approaches based on population genetic signatures \cite{Ross-Ibarra2007}.
Ideally, candidate loci will be identified by first constructing a demographic model representing the history of the domesticate.
In this approach, diversity data from neutral loci are fit to potential models of a crop's demography and then statistical tests of selection are used to identify candidate domestication genes under the most likely model.
Due to the difficulty of this approach and the uncertainty associated with any given demography, many studies identify domestication loci using a strict outlier approach in which loci showing, for example, the greatest reduction in nucleotide diversity or the highest allele frequency differentiation in the domesticate relative to the wild progenitor are identified as candidates.
Introgression during crop expansion may influence candidate gene detection using both demographic-modeling and strict-outlier approaches.
For example, \emph{mexicana} introgression into maize described above accounts for approximately 20\% of the genome of maize in the highlands of Mexico \cite{vanHeerwaarden2011}.
Takuno and co-authors \cite{Takuno2015} have shown that a demographic model incorporating this introgression is a significantly better fit to empirical data than a model lacking introgression.
Failure to account for introgression in maize would therefore compromise domestication candidate detection, particularly if a study contained maize samples from the Mexican highlands.
Likewise, introgression that increased nucleotide diversity in the domesticate or decreased differentiation at domestication loci would confound a strict outlier approach.
However, previous work, also in maize, has shown that known domestication loci are particularly resistant to introgression \cite{hufford2013genomic}, likely due to ongoing selection favoring the domesticated phenotype.

@@

\bibliography{bib_gj.bib}

>>>>

The decreasing cost of genome-wide resequencing and availability of reduced-representation genotyping (\emph{e.g.}, GBS and RAD-Seq), combined with new analytical methods, has facilitated comprehensive study of introgression across a number of species (\textbf{Table 1}). 
%\gmj{Are there newer resequencing methods to discuss here?  DART-Seq, etc?}
%\lwang{I think it is fine to mention two of these methods, it is not our focus.}
High-density marker data can be used with haplotype-based and other methods to assign specific genomic regions to a taxon of origin and identify introgression across taxa \cite{Martin2015,Price2009,Lawson2012,pease2015,rosenzweig2016,geneva2015}.
The methods reviewed here do not include those marginally estimating introgression\slash migration rate as a component of demographic history (\emph{e.g.}, Approximate Bayesian Computation (ABC) \cite{beaumont2002}, diffusion approximations for demographic inference ($\delta a\delta i$) \cite{gutenkunst2009}, isolation with migration models \cite{hey2004}, and a series of methods utilizing the sequentially Markovian coalescent (PSMC, MSMC and SMC++) \cite{li2011, schiffels2014, terhorst2017}). 
Rather, we focus on methods that explicitly identify introgressed genomic segments based on the extent of differentiation, on patterns of nucleotide/haplotype sharing, and phylogenetic relationships.
%We focus here on analytical prospects and limitations and introduce only a few representatives of each category.

First, introgressed segments are expected to show low differentiation from their source population.
The $F_{st}$ and $d_{XY}$ statistics and their derivates including $G_{min}$ \cite{geneva2015} and $RND_{min}$\cite{rosenzweig2016} gauge differentiation. 
The former two statistics are insensitive to rare migrants and therefore lack power to detect recent introgression, while the latter two overcome this limitation.
Additionally, $RND_{min}$ accounts for variable mutation rate, which is detected based on branch length to an outgroup:  $RND_{min} = d_{min}/d_{out}$, where $d_{min}$ is the minimum sequence distance between haplotypes in species X and Y and $d_{out}$ equals $(d_{XO} + d_{YO})/2$, the average sequence distance between each species and the outgroup ($O$).

@@

 %\begin{equation}

 %\end{equation}

@@

%\gmj{Li, are you familiar with the analytical tools MIGRATE-N and BAYESASS?  Rieseberg comapres these two to STRUCTURE at some length in the discussion of this paper:
%https://biology.unm.edu/Whitney/Whitney%20Reprints/Scascitelli%20et%20al%202010.pdf
%Should we include these two methods, even in passing, in this portion of the paper?}
%\lwang{These are more complex statistics to infer the overall demography, like Isolate with migration, which we have defined in the beginning that we will not touch it in the manuscript}

@@

%\gmj{This paragraph about application seems like it might not belong in this section.  Maybe it should be a part of the introduction?  Or, maybe each of these examples could be mentioned directly following the method(s) that was used in the study?}
Application of these approaches combined with population genetic statistics to detect selection across a number of plant and animal species suggests introgression can play an adaptive role.
For example, introgression from ancient hominins (\emph{e.g.}, Neanderthals and Denisovans) to humans has been detected at loci controlling skin pigmentation, defense against pathogens, and toleration of high altitude (reviewed in \cite{Racimo2015});
introgression of wing coloration loci has conferred M\"{u}llerian mimicry
(a type of mimicry in which two unpalatable species resemble one another, compounding the efficacy of their repellant signal)
across butterfly species \cite{Heliconius2012}; introgression has spread insecticide resistance across mosquito species \cite{Norris2015}, and introgression across \emph{Mimulus} (\emph{i.e.}, monkeyflower) species has resulted in adaptation to pollinator preference and contributed to speciation \cite{Stankowski2015}.

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=17.35cm]{./FigsAndTables/Figure1}
	\caption{Hapmix vectors indicating introgression level from \emph{mexicana} to Mexican highland maize on chromosome 4. Data adopted from Hufford et al. \cite{hufford2013genomic}. ELP: EL Porvenir; IXT: Ixtlan ; NAB: Nabogame; OPO: Opopeo; PUR: Puruandiro; SAC: Santa Clara; SAP: San Pedro; TEN: Tenango del Aire; XOC: Xochimilco.}
	\label{fig:introgressionMaize}
\end{figure}

@@

The story of Asian rice (\emph{Oryza sativa}) domestication is still debated, with hybridization between wild and domesticated rice contributing to the complexity of this crop's history.
Certain genetic and archaeobotanical evidence point toward independent domestications of the two prominent varietal groups \emph{japonica} and \emph{indica} from the wild species \emph{Oryza rufipogon} (\emph{rufipogon} hereafter) in the Yangtze Basin of China and the Indian Ganges plain, respectively \cite{fuller2010consilience}.
Other studies support a single domestication occurring 8,200-13,500 BP in the Yangtze Basin, with later divergence of \emph{japonica} and \emph{indica} \cite{molina2011molecular}.
Huang and colleagues \cite{Huang2012} developed a genetic map of rice variation, which they used to measure genetic distance between wild and domesticated rices at and around domesication loci for various geographical locations, finding that \emph{japonica} was likely domesticated in the Pearl River area of Guangxi province, China (just south of the Yangtze Basin), and that \emph{indica} was likely the result of hybridization between \emph{japonica} and local \emph{rufipogon} populations in Southern and South-eastern Asia. %Also, Huang includes the following quote: "We noticed that many loci with strong signals of selection were nearly identical in both indica and japonica where FST between indica and japonica was extremely low, indicating that introduction of traits during domestication has in many cases involved introgression events."

@@

Vaughan and colleagues \cite{vaughan2008evolving} posit a hypothesis combining elements of both theories.
According to this hypothesis, the non-shattering allele arose in a single cultivated rice population and then introgressed into many diverse cultivated populations (some japonica-like, some indica-like) in the region.
This would have facilitated the subsequent spread of other domestication alleles among those populations.
As these domesticated populations then spread into new environments, they would have recieved introgressions from locally-adapted wild relatives, retaining alleles that improved fitness (in agreement with \cite{second1982origin}).
Contemporary populations of wild and domesticated rice show evidence of this history of local adaptation.
The wild relatives \emph{rufipogon} and \emph{nivara} both maintain high genotypic and phenotypic diversity and exhibit locally-adaptive traits (\emph{rufipogon} is adapted to forested wetland environments, whereas \emph{nivara} is adapted to dryer conditions and has life cycle adaptations to survive grazing pressure), suggesting that either offered (and offers) adaptive genetic potential.
Likewise, domesticated rice varieties display patterns of local adaptation (for examples, two of the domesticated rice deepwater varieties (\emph{rayada} and \emph{ashwina}) are said to be selected for the environment along the Ganges river, the \emph{japonicas} are split into temperate and tropical subgroups, and the \emph{indicas} are best suited for lowland environments.

%Other studies support a single center of domestication, arguing that present-day patterns of rice variation could be explained by a single domestication event in a population with high standing variation, followed by dispersal into sympatry with locally-adapted wild relatives in diverse environments, genetic admixture, and selection for adaptive alleles \cite{vaughan2008evolving}.
%The high genetic diversity within domesticated rice is likely due to introgression from wild relatives both within the domestication center(s) and in new environments where rice has dispersed \cite{second1982origin}, and gene flow between domesticated Asian rice and its wild relatives outside of the Yangtze Basin could have imparted locally adaptive traits \cite{vaughan2008evolving}.
%The wild relatives \emph{rufipogon} and \emph{nivara} both maintain high genotypic and phenotypic diversity and exhibit locally-adaptive traits (whereas \emph{rufipogon} is adapted to forested wetland environments, \emph{nivara} is adapted to dryer conditions and has life cycle adaptations to survive grazing pressure).
%From Huang2012, "Based on the SNP data, the sequence diversity (p) of O. rufipogon was estimated at 0.003, which is higher than that in O. sativa—the sequence diversity is 0.0024 for O. sativa, and 0.0016 and 0.0006 for indica and japonica, respectively21".
%Likewise, domesticated rice varieties display patterns of local adaptation (for examples, two of the domesticated rice deepwater varieties (\emph{rayada} and \emph{ashwina}) are said to be selected for the environment along the Ganges river, the \emph{japonicas} are split into temperate and tropical subgroups, and the \emph{indicas} are best suited for lowland environments.
%Gene flow between wild and cultivated rices, though asymmetrical, is frequent enough that nuisance weedy hybrids commonly arise amongst cultivated populations and must be managed with difficulty \cite{vaughan2008evolving}.

To date, research into adaptive introgression in the domestication of rice has been insufficient to detect clearly-supported examples (though \cite{zhao2010genomic} emphasizes the necessity of this research).
%\cite{zhao2010genomic} used a SNP panel and STRUCTURE analysis to uncover patterns of population structure, admixture, and introgression within domesticated rices, and the authors emphasize the importance of similar research that includes wild rice accessions.
There are perhaps some practical reasons why research has not yet been devoted to this inquiry.
As with many other domesticated crops, gene flow between wild and domesticated rices is highly asymmetric (estimates of wild rice admixture in domesticated rice are less than 5 percent \cite{wang2017asian}).
This asymmetry is due in part to the closed floret architecture of the domesticated rice, which hinders outcrossing.
Crop-wild hybridization is frequent enough that nuisance weedy hybrids commonly arise amongst cultivated populations and must be managed with difficulty \cite{vaughan2008evolving}.
During early domestication, introgression may have been more prevalent than at present because barriers to crop-to-wild introgression may have been less severe and because the inbreeding reproductive system of rice would not have been as firmly established \cite{vaughan2008evolving}.
Furthermore, the contemporary distribution of wild rice does not capture the range and diversity of wild rice during early domestication and range expansion of rice.

%Introgression into indica is expected to be more likely than japonica, due to the higher degree of sympatry between indica and its wild relatives.

%note from Asian wild rice is a hybrid swarm with extensive gene flow and feralization from domesticated rice:
%Cite this paper to talk about how the ranges of the several subspecies of domesticated rice are distinct/sometimes overlap.  The paper makes the point that this overlap helps facilitate gene flow.

@@

\rowcolors{2}{white}{gray!25}
\begin{center}
\caption{List and brief description of recently developed methods and examples of empirical studies employing these methods.} \label{tab:tools}
\begin{tabularx}{\textwidth}{llll}
\\\toprule  
\rowcolor{white}
{\bf methods}	& {\bf data type } &	{\bf reference} &  {\bf examples } \\ \midrule

@@

\end{tabularx}
\end{center}
\end{table}

@@

A framework in which crops are domesticated from a single wild population or even a single species is an oversimplification when introgression during the geographic expansion of crops is extensive.
The addition of ongoing gene flow to our understanding of crop demography could bear importantly on fundamental questions of crop domestication:

\subsection*{What is the progenitor of a crop?}
Depending on the extent of post-domestication gene flow with new wild relatives, identification of a crop's progenitor can be complicated or confounded entirely.
Introgression between a crop and newly-encountered populations and species decreases the level of divergence.
This signal could be mistaken for origin rather than gene flow.
%The level of divergence of a crop from newly encountered populations and species will decrease due to introgression, a signal that could be mistaken for origin rather than gene flow.
For example, when determining a single origin of maize from \emph{parviglumis}, Matsuoka and colleagues \cite{matsuoka2002single} identified a paradox: while \emph{parviglumis} is found exclusively in the lowlands of southwest Mexico, maize with allele frequencies most similar to \emph{parviglumis} was found in the highlands of the Mexican Central Plateau.
Several years later, van Heerwaarden \emph{et al.} \cite{vanHeerwaarden2011} resolved the paradox by determining that widespread introgression in the highlands from \emph{mexicana}, which is closely related to \emph{parviglumis}, has caused maize from this region to appear ancestral.
Similarly, extensive post-domestication adaptive introgression from  potato wild relatives long obscured this crop's origin.
Recent work has shown that, following the original domestication event of \emph{Solanum tuberosum} in the central Andes, potato received introgression from as many as four additional species during colonization of the highest elevations of the Andes and the lowlands of the Chilean coast \cite{Spooner2014, Gavrilenko2013}. \gmj{This sentence  needs to be updated with the new potato publication.}

@@

\subsection*{When was a crop domesticated?}
Estimates of the timing of initial domestication are often based on levels of sequence divergence between a crop and populations of its presumed progenitor (\emph{e.g.}, \cite{matsuoka2002single, molina2011molecular}).
In highly introgressed domesticates, these estimates will be based on comparison of either crop or introgressant haplotypes to those of the progenitor.
In such cases, divergence is a mixture of time since domestication and time since split of the progenitor and the introgressing species.
This phenomenon, in combination with divergence of samples from true ancestral populations, ongoing evolution of crop progenitors, and problems with assuming evolution under a molecular clock \cite{Zeder2006}, may explain discrepancies between domestication dates based on genetic and archaeological data.
\lwang{maybe some citations for a protracted domestication time: African rice NG paper, our paper, grape PNAS paper}
More accurate estimates of the timing of domestication may be obtained from genetic data by excluding loci that show signatures of introgression.
\lwang{excluding the introgression regions might cause some inference method not working properly, such as MSMC, as it would reduce heterozygosity.
Suggestions: "More accurate estimates of the timing of domestication may be obtained from genetic data by excluding loci that show signatures of introgression and / or developing new statistic tools which taking potential introgression into account."}

\subsection*{How was genome-wide diversity impacted by a domestication bottleneck?}
\lwang{I suggest to delete "impacted by a domestication bottleneck" because that might confuse readers. Adaptive introgression could affect genome-wide diversity, owing to that introgressing haplotype have a higher historical Ne and domesticates have a lower historical Ne due to bottleneck. Adding "impacted by a domestication bottleneck" seems making the message not direct and not complete.}
Measurement of the strength of the initial domestication bottleneck may also be impacted by adaptive introgression during the spread of crops.
Crop wild relatives have distinct demographies when compared to domesticates and may therefore have contrasting effective population sizes ($N_e$).
The influence of wild relative introgression on estimates of the domestication bottleneck will depend on a number of factors including the magnitude of gene flow, the $N_e$ of the introgressing taxon, and the strength of selection on haplotypes following introgression.
For example, substantial introgression at neutral loci from a wild taxon with a historically higher $N_e$ will lead to underestimates of the overall strength of the domestication bottleneck.
\gmj{Does Li's research fit in well here? Should we add her citation?}

\subsection*{What candidate genes were targeted by selection during domestication?}
Loci targeted by selection during domestication can be identified through so-called ``bottom-up'' approaches based on population genetic signatures \cite{Ross-Ibarra2007}.
Ideally, candidate loci will be identified by first constructing a demographic model representing the history of the domesticate.
In this approach, diversity data from neutral loci are fit to potential models of a crop's demography and then statistical tests of selection are used to identify candidate domestication genes under the most likely model.
Due to the difficulty of this approach and the uncertainty associated with any given demography, many studies identify domestication loci using a strict outlier approach in which loci showing the greatest reduction in nucleotide diversity or the highest allele frequency differentiation in the domesticate relative to the wild progenitor are identified as candidates.
Introgression during crop expansion may influence candidate gene detection using both demographic-modeling and strict-outlier approaches.
For example, \emph{mexicana} introgression into maize described above accounts for approximately 20\% of the genome of maize in the highlands of Mexico \cite{vanHeerwaarden2011}.
Takuno and co-authors \cite{Takuno2015} have shown that a demographic model incorporating this introgression is a significantly better fit to empirical data than a model lacking introgression.
Failure to account for introgression in maize would therefore compromise domestication candidate detection, particularly if a study contained maize samples from the Mexican highlands.
Likewise, introgression that increased nucleotide diversity in the domesticate or decreased differentiation at domestication loci would confound a strict outlier approach.
However, previous work, also in maize, has shown that known domestication loci are particularly resistant to introgression \cite{hufford2013genomic}, likely due to ongoing selection favoring the domesticated phenotype.

@@

\bibliography{bib_gj}
